Using the internal language of toposes in commutative algebra

### 2017-09-16 slides-pssl101.tex
typo

  \hil{Remark.} Same statement for~$A$-modules~$M$ and their mirror
  image~$M^\sim = \underline{M}[\F^{-1}]$.
\end{frame}

\note{\justifying
  The concept of a \emph{prime filter} is a direct axiomatization of what you
  expect the complement of a prime ideal to fulfil. In classical logic,
  complementation gives a bijection between the prime filters and the prime
  ideals of a ring.

>>>>

  \hil{Remark.} The analogous statement holds for~$A$-modules~$M$ and their mirror
  image~$M^\sim = \underline{M}[\F^{-1}]$.
\end{frame}

\note{\justifying
  The concept of a \emph{prime filter} is a direct axiomatisation of what you
  expect the complement of a prime ideal to fulfil. In classical logic,
  complementation gives a bijection between the prime filters and the prime
  ideals of a ring.
